---
title: documentation
editor_options: 
  chunk_output_type: console
---

```{r knitr_config, code=readLines("_knitr_config.R"), echo=FALSE}
```

<!-- ********************************************************************* -->

<!-- > Headline -->

<!-- ********************************************************************* -->

<!-- ## faqs -->

*********************************************************************

## links

* https://realpython.com/documenting-python-code/  
* https://www.datacamp.com/community/tutorials/docstrings-python  
* https://www.python.org/dev/peps/pep-0257/  

*********************************************************************

## Comments

Limit line length for comments and docstrings to 72 characters (https://pep8.org/#maximum-line-length)

### tags

```python
# TODO: asdf
# BUG: asdf
# FIXME: asdf
```

### type hints

* https://www.youtube.com/watch?v=2xWhaALHTvU

```python
def hello(name: str) -> str:
    return(f"Hello {name}")
```

*********************************************************************

### docstring basics

Always use triple double quote string format, even if it's just one line.

The built-in function `help()` prints out the objects docstring to the console.

```{python}
def myfun():
    """A summary line
    
    Further elaboration of the docstring.
    Can be multiple lines.
    """    
    
    print("hello")

myfun.__doc__
help(myfun)
```

*********************************************************************

## docstring types

### class docstrings

```python
class MyClass:
    """
    Brief summary of purpose and behaviour
    ...

    Attributes
    ----------
    attribute1 : str
        an attribute
    attribute2 : str
        another attribute

    Methods
    -------
    a_method
        Prints attribute2
    """

    attribute1 = "asdf"
    
    def __init_(self, attribute2: str):
        """
        Parameters
        ----------
        attribute2 : str
            another attribute
            
        Raises
        ------
        NotImplementedError
            If no sound is set for the animal or passed in as a
            parameter.
            
        """
        
        self.attribute2 = attribute2

    def a_method(self):
        """Prints attribute2"""

        print(self.attribute1)
```

### function, module and package docstrings

#### function

* should include the same items as a class method:
  * a brief description of what the function is and what it’s used for  
  * any arguments (both required and optional) that are passed including keyword arguments  
  * label any arguments that are considered optional  
  * any side effects that occur when executing the function  
  * any exceptions that are raised  
  * any restrictions on when the function can be called  

#### module

* similar to class docstrings  
* placed at the top of the file even before any imports  
* should include:  
  * a brief description of the module and its purpose  
  * a list of any classes, exception, functions, and any other objects exported by the module

#### package

* should be placed at the top of the package’s `__init__.py` file  
* should list the modules and sub-packages that are exported by the package

### script docstrings

* placed at the top of the file  
* should be documented well enough for users to be able to have a sufficient understanding of how to use the script  
* should be usable for its “usage” message, when the user incorrectly passes in a parameter or uses the -h option

```{r, opts.label="cat_file"}
cat_file("hello.py")
```

```{sh}
python hello.py you
```

This bit doesn't work...

```{sh}
python hello.py -h
```

#### argparse

* if you use `argparse` you can omit parameter-specific documentation  
  * make sure you document it filly in the `argparser.parser.add_argument` function  
  * recommended to use the `__doc__` for the description parameter within `argparse.ArgumentParser` constructor. 
  * any custom or third-party imports should be listed to allow users to know which packages may be required for running the script
  
*********************************************************************

## docstring formats

### NumPy/SciPy

### Google

*********************************************************************

## documenting projects



