---
title: TODO
editor_options: 
  chunk_output_type: console
---

```{r knitr_config, code=readLines("_knitr_config.R"), echo=FALSE}
```

*********************************************************************

* https://www.datacamp.com/community/tutorials/reading-writing-files-python

*********************************************************************

```python
fh = open(filepath, mode) # returns a file object called a handle
```

mode | description
------------- | -------------
r | Read (default)
w | Write; creates a new file (erasing the data for any file with the same name)
x | Write; creates a new file, but fails if the file path already exists
a | Append to existing file (create the file if it does not already exist)
r+ | Read and write
b | Add to mode for binary files (i.e., 'rb' or 'wb')
t | Text mode for files (automatically decoding bytes to Unicode). This is the default if not specified. Add t to other modes to use this (i.e., 'rt' or 'xt')

```{sh, cache=FALSE}
echo 'line 1\nline 2\nline 3' > temp.txt
cat temp.txt
```

```{python}
fh = open("temp.txt", "r")
fh.name
fh.mode
fh.close()
```

Using `with` means you don't have to explicitly close the file hand.

```python
with open("temp.txt", "r") as fh:
    ...
```

*********************************************************************

## reading

### read

Reads everything by default - returns a string.

```{python}
with open("temp.txt", "r") as fh:
    out = fh.read()
out
print(out)
```

Specify the number of characters to read

```{python}
with open("temp.txt", "r") as fh:
    out = fh.read(2)
print(out)
```

### readline

Reads one line at a time

```{python}
with open("temp.txt", "r") as fh:
    print(fh.readline(), end='')
    print(fh.readline(), end='')
    print(fh.readline(), end='')
```

Specify the number of characters to print

```{python}
with open("temp.txt", "r") as fh:
    print(fh.readline(3))
    print(fh.readline(4))
    print(fh.readline(3))
    print(fh.readline(4))
    print(fh.readline(3))
    print(fh.readline(4))
```

Alternatively, 

```{python}
with open("temp.txt", "r") as fh:
    for line in fh:
        print(line, end='')
```

### readlines

Reads everything and returns a list of strings (one line per element).

```{python}
with open("temp.txt", "r") as fh:
    out = fh.readlines()
print(out)
```

Specify the number of lines to read

```{python}
with open("temp.txt", "r") as fh:
    out = fh.readlines(2)
print(out)
```

*********************************************************************

## writing

### write

```{python, cache=FALSE}
with open("temp.txt", "a") as fh:
    fh.write("line 4\n")
    fh.write("line 5\n")
with open("temp.txt", "r") as fh:
    print(fh.read())
```

```{python, cache=FALSE}
lines = ['line 6\n', 'line 7\n']
with open("temp.txt", "a") as fh:
    for line in lines:
        fh.write(line)
with open("temp.txt", "r") as fh:
    print(fh.read())
```

### writelines

*********************************************************************

## copying

```{python, cache=FALSE}
with open("temp.txt", "r") as readfile:
    with open("temp2.txt", "w") as writefile:
        for line in readfile:
            writefile.write(line)
with open("temp2.txt", "r") as fh:
    print(fh.read())
```

*********************************************************************

## misc 

```python
fh.seek(offset,reference_point) # the reference points are 0 (the beginning of the file and is default), 1 (the current position of file) and 2 (the end of the file).
fh.tell()
fh.truncate()
fh.next()
fh.flush()
```

*********************************************************************

```{r, cache=FALSE, echo=FALSE}
system("rm temp.txt")
system("rm temp2.txt")
```


