---
title: sys
editor_options: 
  chunk_output_type: console
---

```{r knitr_config, code=readLines("_knitr_config.R"), echo=FALSE}
```

*********************************************************************

> System-specific parameters and functions

*********************************************************************

* https://python.readthedocs.io/en/latest/library/sys.html

*********************************************************************

## command line args

The list of command line arguments passed to a Python script. 

argv[0] is the script name (it is operating system dependent whether this is a full pathname or not). If the command was executed using the -c command line option to the interpreter, argv[0] is set to the string '-c'. If no script name was passed to the Python interpreter, argv[0] is the empty string.

```{sh, cache=FALSE}
echo 'import sys
for i in range(len(sys.argv)):
    print("sys.argv[" + str(i) + "] = \"" + sys.argv[i] + "\"")
' > 'temp.py'
```

```{sh, cache=FALSE}
python temp.py a b
```

```{r, cache=FALSE, echo=FALSE}
system("rm temp.py")
```

*********************************************************************

## path

* `path`: the list of directories Python searches through to find for modules and files 
* stored as a list in `sys.path` - can therefore use list methods to modify it  

```{python}
import sys
from pprint import pprint
type(sys.path)
pprint(sys.path)
```

E.g. 

```python
sys.path.append('extrapath') 
sys.path.extend(['extrapath'])
sys.path.insert(0, 'extrapath')
```

*********************************************************************

## python version

```{python}
import sys
sys.version
sys.prefix
sys.executable
```

*********************************************************************

## os

```{python}
import sys
sys.platform
```

`linux` = Linux  
`win32` = Windows  
`cygwin` = Windows/Cygwin  
`darwin` = Mac OS X  






